---
title: "Imports OLD Transplant Data Rnotebook"
output: html_notebook
---

Goals:

#1 Import data from REDCap
#2 Identify subjects missing values
#3 Clean existing data 
#4 Align with newer version of REDCap
#5 Export data and unite with NEW REDCap project/data.

## Load Libraries and set global constants
```{r Loading Libraries, echo=FALSE}
library(RCurl)
library(jsonlite)
library(dplyr)
```
```{r Constants and Definitions}
api_url='https://redcap.partners.org/redcap/api/'
txp_token1= '733D673904E7A34A7BCCFE6B789AC276'
ClinGen_token= '988B6AE24F596A66026E82D50D0796FB'
PPMR_token= '5D09F30900B9FA4EFA667E684D22B8C1'
```
# PPMR Data from REDCap
## Import JSON data from REDCap using API access
```{r Data Import module - PPMR}
work.PPMR = postForm(
    uri=api_url,
    token=PPMR_token,
    content='record',
    format='json',
    type='flat',
    'fields[0]'='subject_id',
    'fields[1]'='log_transplant_id',
    'fields[2]'='transp_cons_dat',
    'fields[3]'='dob_log',
    rawOrLabel='raw',
    rawOrLabelHeaders='raw',
    exportCheckboxLabel='false',
    exportSurveyFields='false',
    exportDataAccessGroups='false',
    returnFormat='json',
    filterLogic='[transplant_cons(1)] = 1'
)
PPMR = fromJSON(work.PPMR)
PPMR = rename(PPMR,TransplantID = log_transplant_id, PPMR_ID = subject_id, ConsentDATE = transp_cons_dat, DOB = dob_log)  
PPMR = select(PPMR, PPMR_ID,TransplantID, ConsentDATE, DOB)
```

# Transplant Study Data from *OLD* REDCap DB
## Imports JSON data using API
```{r Data Import module - Transplant}
work.txp1 = postForm(
    uri= api_url,
    token= txp_token1,
    content='record',
    format='json',
    type='flat',
    rawOrLabel='raw',
    rawOrLabelHeaders='raw',
    exportCheckboxLabel='false',
    exportSurveyFields='false',
    exportDataAccessGroups='false',
    returnFormat='json'
)
txp1= fromJSON(work.txp1)



```

```{r PPMI Transplant Study REDCap}
work.txp_temp3 <- postForm(
    uri='https://redcap.partners.org/redcap/api/',
    token='F693D1C3E97B6F591F9A3CF50B40B1F2',
    content='record',
    format='json',
    type='flat',
    'fields[0]'='transplant_id',
    'fields[1]'='elig_dx',
    'fields[2]'='herlihy_questionnaire_complete',
    'fields[3]'='pgc_supplemental_questionnaire_pgcqs_complete',
    'fields[4]'='pulmonary_genetics_center_questionnaire_pgcq_complete',
    'fields[5]'='st_georges_questionnaire_sgrq_copd_complete',
    'fields[6]'='st_georges_questionnaire_sgrqiipf_complete',
    'events[0]'='baseline_arm_1',
    rawOrLabel='raw',
    rawOrLabelHeaders='raw',
    exportCheckboxLabel='false',
    exportSurveyFields='false',
    exportDataAccessGroups='false',
    returnFormat='json'
)
work.txp3= fromJSON(work.txp_temp3)
work.txp3$PGCS_Status = work.txp3$pgc_supplemental_questionnaire_pgcqs_complete
work.txp3$PGC_Status = work.txp3$pulmonary_genetics_center_questionnaire_pgcq_complete
work.txp3$Herlihy_Status = work.txp3$herlihy_questionnaire_complete
work.txp3$SGRQ_Status = ifelse(work.txp3$st_georges_questionnaire_sgrqiipf_complete== 2 | work.txp3$st_georges_questionnaire_sgrq_copd_complete== 2, 2,0)
work.txp3$TransplantID = work.txp3$transplant_id
```
```{r Creates PPMI transplant DB}
txp_A = merge(temp.txp, PPMR, by.x = "record_id", by.y = "PPMR_ID", all.y = TRUE)
txp = merge(txp_A, work.txp3, by ="TransplantID", all.x = TRUE)

txp$PGC_Status = ifelse(is.na(txp$PGC_Status.x),
                             ifelse(is.na(txp$PGC_Status.y),0,
                                    txp$PGC_Status.y),
                             ifelse(txp$PGC_Status.x == 0,
                                    ifelse(!is.na(txp$PGC_Status.y),
                                           txp$PGC_Status.y,txp$PGC_Status.x),
                                    txp$PGC_Status.x))

txp$Herlihy_Status = ifelse(is.na(txp$Herlihy_Status.x),
                             ifelse(is.na(txp$Herlihy_Status.y),0,
                                    txp$Herlihy_Status.y),
                             ifelse(txp$Herlihy_Status.x == 0,
                                    ifelse(!is.na(txp$Herlihy_Status.y),
                                           txp$Herlihy_Status.y,txp$Herlihy_Status.x),
                                    txp$Herlihy_Status.x))

txp$SGRQ_Status = ifelse(is.na(txp$SGRQ_Status.x),
                             ifelse(is.na(txp$SGRQ_Status.y),0,
                                    txp$SGRQ_Status.y),
                             ifelse(txp$SGRQ_Status.x == 0,
                                    ifelse(!is.na(txp$SGRQ_Status.y),
                                           txp$SGRQ_Status.y,txp$SGRQ_Status.x),
                                    txp$SGRQ_Status.x))

txp = select(txp,TransplantID,MRN,PGC_Status,Herlihy_Status,SGRQ_Status,PGCS_Status,TransplantStudy,emailAVAIL,email,elig_dx,Deceased)
```

# Clinical Genetics Study Data
## Imports JSON data using API
```{r Data Import module - Clinical Genetics}
work1.ILD = postForm(
    uri=api_url,
    token=ClinGen_token,
    content='record',
    format='json',
    type='flat',
    'fields[0]'='bwhild_id',
    'fields[1]'='id',
    'fields[2]'='mrn',
    'fields[3]'='familyid',
    'fields[4]'='familyname',
    'fields[5]'='demo_last',
    'fields[6]'='herlihy_questionnaire_complete',
    'fields[7]'='st_georges_respiratory_questionnaire_sgrq_complete',
    'fields[8]'='pulmonary_genetics_questionnaire_complete',
    rawOrLabel='raw',
    rawOrLabelHeaders='raw',
    exportCheckboxLabel='false',
    exportSurveyFields='false',
    exportDataAccessGroups='false',
    returnFormat='json',
    filterLogic='[icf_signature(4)] = 1'
)

work2.ILD = fromJSON(work1.ILD)
work2.ILD$arm = ifelse(work2.ILD$redcap_event_name == "screening_arm_1","proband",
                 ifelse(work2.ILD$redcap_event_name == "screening_arm_2","relatives","ERROR"))
work2.ILD$ClinicalGeneticsStudy = TRUE
work2.ILD$LastName = toupper(work2.ILD$demo_last)
work2.ILD$FamilyNAME = toupper(work2.ILD$familyname)
work2.ILD$MRN = work2.ILD$mrn
work2.ILD$FamilyID = work2.ILD$familyid
work2.ILD$id[work2.ILD$id == ""] = work2.ILD$bwhild_id[work2.ILD$id == ""] #replaces missing values of "id" using values from "bwhwork2.ILD_id"
work2.ILD = work2.ILD[,!(names(work2.ILD) %in% c("mrn","familyid","familyname","demo_last"))] #drops original variables not capitalized
#work2.ILD$ProbandID[,work2.ILD$arm == "relatives"] = work2.ILD$id[,work2.ILD$arm == "proband" & work2.ILD$]

ILD_relatives = subset(work2.ILD, work2.ILD$arm == "relatives")
DF_FamilyIDs = unique(ILD_relatives[c("FamilyNAME","FamilyID")])
ILD_probands = subset(work2.ILD,work2.ILD$arm == "proband")
ILD_probands = ILD_probands[,!(names(ILD_probands) %in% c("FamilyID"))] #drops unused variable FamilyILD
ILD_probands$probandID = ILD_probands$id
ILD_pro2 = ILD_probands[c("probandID","LastName")]
ILD_pro2$LastName[ILD_pro2$LastName == "BURHAM"] = "BURNHAM" #corrects mispelling of name
ILD_pro3 = merge(ILD_probands, DF_FamilyIDs, by.x = "LastName", by.y = "FamilyNAME",all = TRUE)
ILD_rel2 = merge(ILD_relatives, ILD_pro2, by.x= "FamilyNAME", by.y=
              "LastName", all.x= TRUE)
ILD_pro3$probandID = NA #resets before merge because we dont need this for probands
ILD_all = rbind(ILD_rel2,ILD_pro3)
ILD = subset(ILD_all, ILD_all["arm"]=="proband")
ILD$ClinGen = 1
ILD$PGC_Status = ILD$pulmonary_genetics_questionnaire_complete
ILD$Herlihy_Status = ILD$herlihy_questionnaire_complete
ILD$SGRQ_Status = ILD$st_georges_respiratory_questionnaire_sgrq_complete
KEEP = c("MRN","id","PGC_Status","Herlihy_Status","SGRQ_Status","ClinicalGeneticsStudy")
ILD = ILD[KEEP]
```


# Create lists of variables per domain and instrument
```{r Define Herlihy Domains}
Herlihy_domains = c("Herlihy_demos","Herlihy_CC","Herlihy_Symptom_Severity","Herlihy_Symptom_Severity","Herlihy_Symptom_Oxygen","Herlihy_AcuteAxacerbations","Herlihy_DC_symptoms","Herlihy_Symptom_Constitutional","Herlihy_CardPulm","Herlihy_Symptoms_Digestive","Herlihy_Rheumatology","Herlihy_Skin","Herlihy_Allergies","Herlihy_SocialHistory_TobaccoHx","Herlihy_SocialHistory_EtOH_drugs","Herlihy_SocialHistory_Lifestyle","Herlihy_research_admin")

Herlihy_demos = c("record_id_0","first_name","last_name","address","telephone_1",
                  "telephone_2","referrring_physician","first_name1","last_name2",
                  "telephone","physician_address","email",
                  "brigham_and_womens_hospital_number",
                  "list_any_other_physicians_you_are_currently_see","date_of_birth_0",
                  "place_of_birth","birth_address","sex","ethnic_group")
Herlihy_CC = c("what_are_the_main_concerns_that_prompted_your_visit_today")

Herlihy_Symptom_Severity = c("do_you_usually_have_a_cough","do_you_usually_bring_up_phlegm_from_your_chest","have_you_had_a_cough_with_phlegm_on_most_days_for_at_least_3_months_per_year_for_the_past_two_years","do_you_ever_cough_up_blood","do_you_get_short_of_breath","do_you_get_short_of_breath_when_you_are_climbing_stairs","how_many_steps_can_you_climb_before_you_get_short_of_breath",
"for_how_long_have_you_been_short_of_breath","how_far_can_you_walk_on_a_flat_surface_before_you_become_short_of_breath","are_you_short_of_breath_when_showering_or_dressing_cooking_or_doing_light_housework","do_you_require_assistance_with_these_activities_showering_dressing_cooking_or_light_house_work")

Herlihy_Symptom_Oxygen = c("do_you_need_to_use_oxygen","do_you_need_to_use_oxygen_with_exercise",
"how_many_liters_per_minute_of_oxygen_do_you_need_during_exercise",
"do_you_need_to_use_oxygen_with_sleep",
"how_many_liters_per_minute_of_oxygen_do_you_need_during_sleep",
"do_you_need_to_use_oxygen_at_rest",
"how_many_liters_per_minute_of_oxygen_do_you_need_during_rest",
"how_long_have_you_been_using_oxygen_",
"do_you_use_either_of_the_following_for_breathing_assistance_with_sleep_or_during_the_day")

Herlihy_AcuteExacerbations = c("year_have_you_been_to_the_emergency_room_or_hospitalized_for_lung_problems",
"emergency_room_or_hospitalized_for_lung_problems_in_the_past_year",
"in_the_past_year_an_intensive_care_unit_icu_for_your_breathing",
"how_many_times_in_an_intensive_care_unit_icu_for_your_breathing_in_the_past_year",
"in_the_past_year_have_you_been_placed_on_a_breathing_machine_for_your_lung_disease",
"how_many_times_have_you_been_placed_on_a_breathing_machine_for_your_lung_disease_in_the_past_year","in_the_past_year_have_you_been_treated_with_antibiotics_for_a_chest_illness",
"how_many_times_have_you_been_treated_with_antibiotics_for_a_chest_illness_in_the_past_year_","treated_with_steroid_pills_or_injections_such_as_prednisone_or_solumedrol_for_a_chest_illness","times_steroid_pills_or_injections_for_a_chest_illness_in_the_past_year",
"have_you_ever_had_any_chest_operations","what_type_of_chest_operation_have_you_had")

Herlihy_DC_symptoms = c("do_you_have_fever",
"do_you_have_chills","do_you_have_sweats","do_you_sweat_during_the_night",
"do_you_get_headaches","do_you_notice_any_change_in_your_in_your_vision_beforeduringafter_the_headaches","do_you_notice_any_numbness_or_weakness_beforeduringafter_the_headaches",
"do_you_notice_any_fever_or_stiff_neck_with_your_headaches","have_you_had_nausea_or_vomiting_of_food_or_fluids","do_you_suffer_from_constipation","for_how_long_have_you_been_tired",
"do_you_feel_tired_all_day","have_you_noticed_any_change_in_your_mood","have_you_noticed_any_change_in_your_concentration","have_you_noticed_any_change_in_you_sexual_desire",
"have_you_noticed_any_change_in_interests","do_you_have_abnormal_sleep","how_many_hours_per_night_do_you_sleep","do_you_nap_during_the_day","how_many_hours_do_you_nap_for","previous_hospitalizations_andor_surgeries","previous_hospitalizations_and_or_surgeries","have_you_had_any_allergic_reaction_to_food","please_specify_the_food_you_have_had_allergic_reaction_to","what_type_of_work_do_you_do","have_you_ever_been_exposed_to_environmental_hazards",
"what_have_you_been_exposed_to","how_many_times_per_week_do_you_exercise","have_you_ever_been_vaccinated_against_influenza","have_you_ever_received_the_pneumonia_vaccine",
"please_fill_out_the_chart_below_on_your_family_history_of_each_illness","going_for_walks_or_walking_the_dog","doing_activities_or_chores_at_home_or_in_the_garden","having_sexual_intercourse","going_to_church_or_a_place_of_entertainment","going_out_in_bad_weather_or_into_smoky_rooms","visiting_family_or_friends_or_playing_with_children","lungrespiratory_problem_may_stop_you_from_doing","describes_how_your_breathing_problem_affects_you")

Herlihy_Symptom_Constitutional = c("have_you_noticed_any_change_with_your_weight_in_the_last_year","did_you_lose_weight_or_gain_weight_in_the_last_year","how_many_pounds_did_you_gainlose","over_what_period_of_time_did_your_weight_change_","was_the_weight_gainloss_intentional","have_you_been_tired")

Herlihy_CardPulm = c("do_you_have_to_prop_yourself_up_on_pillows_to_sleep_at_night",
"have_you_noticed_any_fluid_retention_around_your_ankles")

Herlihy_Symptoms_Digestive = c("do_you_have_heartburn","does_food_or_drink_get_stuck_when_you_are_eating_or_do_you_have_difficulty_swallowing","do_you_cough_or_choke_when_eating","do_you_have_pain_with_taking_a_deep_breath")

Herlihy_Rheumatology = c(
"do_you_have_any_painful_joints_in_your_body","have_you_ever_felt_morning_stiffness",
"have_you_noticed_any_rash","have_you_felt_muscle_weakness",
"have_you_had_canker_sores_in_your_mouth","has_your_skineyes_been_dry",
"have_you_noticed_dry_mouth","do_you_suffer_from_recurrent_nose_bleeds",
"do_you_suffer_from_sinus_pain_or_recurrent_sinus_infections",
"have_you_ever_had_painful_or_swollen_joints","do_you_have_muscle_weakness",
"has_it_become_difficult_to_open_your_mouth")

Herlihy_Skin = c(
  "do_you_burn_easily_in_the_sun","do_your_hands_turn_white_blur_or_red_in_the_cold",
"does_cold_temperature_bother_you","have_you_been_losing_your_hair")

Herlihy_Allergies = c(
  "have_you_had_any_allergic_reaction","have_you_had_any_allergic_reaction_to_medications",
"please_specify_the_medications_you_have_had_allergic_reaction_to","have_you_had_any_allergic_reaction_to_dust","have_you_had_any_allergic_reaction_to_","please_specify_which_you_have_had_allergic_reaction_to","other_allergies")

Herlihy_SocialHistory_TobaccoHx = c("have_you_ever_smoked_cigarettes",
"at_what_age_did_you_start_smoking_regularly",
"on_average_how_many_packs_per_day_did_you_smoke",
"are_you_smoking_cigarettes_now",
"at_what_age_did_you_stop_smoking_cigarettes",
"have_you_ever_smoked_cigars",
"on_average_how_many_cigars_per_day",
"are_you_smoking_cigars_now",
"have_you_ever_smoked_tobacco_using_a_pipe",
"how_many_times_dodid_you_smoke_tobacco_using_a_pipe_per_day",
"are_you_smoking_a_pipe_now",
"does_anyone_besides_you_regularly_smoke_within_your_home")

Herlihy_SocialHistory_EtOH_drugs = c("do_you_drink_alcohol",
"how_many_drinks_do_you_have_per_week","do_you_drink_alcohol",
"how_many_drinks_do_you_have_per_week")

Herlihy_SocialHistory_Lifestyle = c("do_you_exercise_regularly","what_type_of_exercise_do_you_do","have_you_ever_owned_any_birds","have_you_ever_owned_other_pets")

Herlihy_research_admin = c("receiving_information_regarding_our_research_activities",
"interst_in_studies_at_bwh")
```


```{r Define PGC Domains}
Herlihy_domains = c("PGC_demos","PGC_Other_med_hx","PGC_template","PGC_medications","PGC_SocialHistory_TobaccoHx","PGC_Exposures","PGC_Participant_ancestery","PGC_Mother_ancestery","PGC_Mother_MedHx", "PGC_Father_ancestery","PGC_Father_MedHx", "PGC_Grandparents_MedHx", "PGC_Children_MedHx", "PGC_Sibling_MedHx", "PGC_AuUncle_MedHx", "PGC_Other_info")

PGC_demos = c("patient_name","date_of_birth","age","form_completed_by","relationship_to_patient")

PGC_symptoms = c("reasons_for_visit","patient_following_symptoms___0","patient_following_symptoms___1","patient_following_symptoms___2","patient_following_symptoms___3","patient_following_symptoms___4","patient_following_symptoms___5","patient_following_symptoms___6",
"patient_following_symptoms___7","patient_following_symptoms___8","patient_following_symptoms___9","patient_following_symptoms___10","patient_following_symptoms___11","patient_following_symptoms___12","how_long_symptoms","additional_symptoms1___0","additional_symptoms1___1","additional_symptoms1___2","additional_symptoms1___3","additional_symptoms2___0","additional_symptoms2___1","additional_symptoms2___2","additional_symptoms2___3","additional_symptoms2___4","additional_symptoms3___0","additional_symptoms3___1","additional_symptoms3___2","additional_symptoms3___3","additional_symptoms4___0","additional_symptoms4___1","additional_symptoms4___2","additional_symptoms4___3","additional_symptoms5___0","additional_symptoms5___1","additional_symptoms6___0","additional_symptoms6___1","additional_symptoms6___2","additional_symptoms6___3","additional_symptoms7","how_many_medical_problems1___1","how_many_medical_problems1___2","how_many_medical_problems1___3","how_many_medical_problems2___0","how_many_medical_problems2___1","how_many_medical_problems2___2","how_many_medical_problems2___3",
"how_many_medical_problems2___4","how_many_medical_problems2___5","how_many_medical_problems2___6","how_many_medical_problems2___7","how_many_medical_problems2___8","how_many_medical_problems2___9","how_many_medical_problems2___10","how_many_medical_problems2___11",
"how_many_medical_problems2___12","how_many_medical_problems2___13","how_many_medical_problems2___14","how_many_medical_problems2___15","how_many_medical_problems2___16",
"how_many_medical_problems2___17","how_many_medical_problems2___18","how_many_medical_problems3___0","how_many_medical_problems3___1","how_many_medical_problems3___2","how_many_medical_problems3___3","how_many_medical_problems3___4","how_many_medical_problems3___5",
"how_many_medical_problems4___0","how_many_medical_problems4___1","how_many_medical_problems4___2","how_many_medical_problems5___0","how_many_medical_problems5___1","how_many_medical_problems5___2","how_many_medical_problems5___3","how_many_medical_problems5___4","how_many_medical_problems6___0","how_many_medical_problems6___1","how_many_medical_problems6___2",
"how_many_medical_problems6___3","how_many_medical_problems6___4","how_many_medical_problems7___0","how_many_medical_problems7___1","how_many_medical_problems7___2","how_many_medical_problems7___3","how_many_medical_problems7___4","how_many_medical_problems8___0","how_many_medical_problems8___1","how_many_medical_problems8___2","how_many_medical_problems8___3",
"how_many_medical_problems8___4","how_many_medical_problems8___5","how_many_medical_problems9___0","how_many_medical_problems9___1","how_many_medical_problems9___2","how_many_medical_problems9___3","how_many_medical_problems9___4","how_many_medical_problems10___0","how_many_medical_problems10___1","how_many_medical_problems10___2")


PGC_Other_med_hx = c("patient_allergies___0","patient_allergies___1","patient_allergies___2","patient_allergies___3","patient_vaccines___0","patient_vaccines___1")

PGC_medications = c("current_medications1___0","current_medications2","current_medications3","current_medications4","current_medications5")
## IF current_medications1___0 = 1 then section complete

PGC_SocialHistory_TobaccoHx = c("tobacco_history1___0","tobacco_history1___1","tobacco_history2","tobacco_history3",
"tobacco_history4","tobacco_history5___0","tobacco_history5___1","tobacco_history5___2",	"tobacco_history5___3")

PGC_Exposures = c("patients_environment2___0","patients_environment2___1",
"patients_environment2___2","patients_environment3___0","patients_environment3___1",
"patients_environment3___2","patients_environment3___3","patients_environment4___0",
"patients_environment4___1","patients_environment4___2","patients_environment4___3",
"patients_environment5___0","patients_environment5___1","patients_environment5___2",
"patients_environment6","patients_environment7")

PGC_Participant_ancestery = c("patient_ancestry1___0","patient_ancestry1___1","patient_ancestry1___2",
"patient_ancestry1___3","patient_ancestry1___4","patient_ancestry1___5","patient_ancestry1___6","patient_ancestry1___7","patient_ancestry1___8","patient_ancestry1___9",
"patient_ancestry1___10","patient_ancestry2")

PGC_Mother_ancestery = c("patient_ancestry4","patient_ancestry5","patient_ancestry6",
"patient_ancestry7","patient_ancestry8","patient_ancestry9")

PGC_template = c("lung_diseases___0","lung_diseases___1","lung_diseases___2","lung_diseases___3","lung_diseases___4","lung_diseases___5","lung_diseases___6","lung_diseases___7",
"lung_diseases___8","lung_diseases___9","lung_diseases___10","lung_diseases___11","lung_diseases___12","lung_diseases___13","lung_diseases___14","lung_diseases___15","lung_diseases___16","lung_diseases___17","age2___0","age2___1","age2___2","age2___3","age2___4","age2___5",
"age2___6","age2___7","age2___8","age2___9","age2___10","age2___11","age2___12","elaborate")

PGC_Mother_MedHx = c("biological_parents_chart2___0","biological_parents_chart2___1",
"biological_parents_chart3","biological_parents_chart4___0","biological_parents_chart4___1",
"biological_parents_chart5","biological_parents_chart6","biological_parents_chart7")

PGC_Father_ancestery = c("patient_ancestry10","patient_ancestry11","patient_ancestry12",
"patient_ancestry13","patient_ancestry14","patient_ancestry15")

PGC_Father_MedHx = c("biological_parents_chart8___0","biological_parents_chart8___1",
"biological_parents_chart9","biological_parents_chart10___0","biological_parents_chart10___1","biological_parents_chart11","biological_parents_chart12","biological_parents_chart13")

PGC_Grandparents_MedHx = c("biological_grandparents_chart2___0","biological_grandparents_chart2___1","biological_grandparents_chart3","biological_grandparents_chart4___0","biological_grandparents_chart4___1",
"biological_grandparents_chart6","biological_grandparents_chart7","briological_grandparents_chart8","biological_grandparents_chart9___0","biological_grandparents_chart9___1",
"biological_grandparents_chart10","bological_grandparents_chart11___0","bological_grandparents_chart11___1","biological_grandparents_chart12","biological_grandparents_chart13",
"biological_grandparents_chart14","biological_grandparents_chart15___0","biological_grandparents_chart15___1","biological_grandparents_chart16","biological_grandparents_chart17___0",
"biological_grandparents_chart17___1","biological_grandparents_chart18","biological_grandparents_chart19","biological_grandparents_chart20","biological_grandparents_chart21___0",
"biological_grandparents_chart21___1","biological_grandparents_chart22","biological_grandparents_chart23___0","biological_grandparents_chart23___1","biological_grandparents_chart24",
"biological_grandparents_chart25","biological_grandparents_chart26")

PGC_Children_MedHx = c("biological_children_chart2","biological_children_chart3___0",
"biological_children_chart3___1","biological_children_chart4___0","biological_children_chart4___1","biological_children_chart5","biological_children_chart6___0","biological_children_chart6___1","biological_children_chart7","biological_children_chart8","biological_children_chart9","biological_children_chart10","biological_children_chart11___0","biological_children_chart11___1","biological_children_chart12___0","biological_children_chart12___1","biological_children_chart13","biological_children_chart14___0","biological_children_chart14___1","biological_children_chart15","biological_children_chart16","biological_children_chart17","biological_children_chart18","biological_children_chart19___0","biological_children_chart19___1","biological_children_chart20___0","biological_children_chart20___1","biological_children_chart21","biological_children_chart22___0","biological_children_chart22___1","biological_children_chart23","biological_children_chart24","biological_children_chart25","biological_children_chart26","biological_children_chart27___0","biological_children_chart27___1","biological_children_chart28___0","biological_children_chart28___1","biological_children_chart29","biological_children_chart30___0","biological_children_chart30___1","biological_children_chart31","biological_children_chart32","biological_children_chart33","biological_children_chart34","biological_children_chart35___0","biological_children_chart35___1","biological_children_chart36___0","biological_children_chart36___1","biological_children_chart37","biological_children_chart38___0","biological_children_chart38___1","biological_children_chart39","biological_children_chart40","biological_children_chart41")

PGC_Sibling_MedHx = c("biological_siblings_chart2","biological_siblings_chart3___0","biological_siblings_chart3___1","biological_siblings_chart4___0","biological_siblings_chart4___1",
"biological_siblings_chart5","biological_siblings_chart6___0","biological_siblings_chart6___1","biological_siblings_chart7","biological_siblings_chart8","biological_siblings_chart9",
"biological_siblings_chart10","biological_siblings_chart11___0","biological_siblings_chart11___1","biological_siblings_chart12___0","biological_siblings_chart12___1","biological_siblings_chart13","biological_siblings_chart14___0","biological_siblings_chart14___1","biological_siblings_chart15","biological_siblings_chart16","biological_siblings_chart17","biological_siblings_chart18","biological_siblings_chart19___0","biological_siblings_chart19___1","biological_siblings_chart20___0","biological_siblings_chart20___1","biological_siblings_chart21",
"biological_siblings_chart22___0","biological_siblings_chart22___1","biological_siblings_chart23","biological_siblings_chart24","biological_siblings_chart25","biological_siblings_chart26","biological_siblings_chart27___0","biological_siblings_chart27___1",
"biological_siblings_chart28___0","biological_siblings_chart28___1","biological_siblings_chart29","biological_siblings_chart30___0","biological_siblings_chart30___1","biological_siblings_chart31","biological_siblings_chart32","biological_siblings_chart33","biological_siblings_chart34","biological_siblings_chart35___0","biological_siblings_chart35___1","biological_siblings_chart36___0","biological_siblings_chart36___1","biological_siblings_chart37","biological_siblings_chart38___0","biological_siblings_chart38___1","biological_siblings_chart39",
"biological_siblings_chart40","biological_siblings_chart41","biological_siblings_chart42___0","biological_siblings_chart42___1","biological_siblings_chart43")

PGC_AuUncle_MedHx = c("biological_aunts_uncles_chart2","biological_aunts_uncles_chart3___0",
"biological_aunts_uncles_chart3___1","biological_aunts_uncles_chart4___0","biological_aunts_uncles_chart4___1","biological_aunts_uncles_chart5","biological_aunts_uncles_chart6___0",
"biological_aunts_uncles_chart6___1","biological_aunts_uncles_chart7",
"biological_aunts_uncles_chart8","biological_aunts_uncles_chart9","biological_aunts_uncles_chart10","biological_aunts_uncles_chart11___0","biological_aunts_uncles_chart11___1",
"biological_aunts_uncles_chart12___0","biological_aunts_uncles_chart12___1",
"biological_aunts_uncles_chart13","biological_aunts_uncles_chart14___0",
"biological_aunts_uncles_chart14___1","biological_aunts_uncles_chart15",
"biological_aunts_uncles_chart16","biological_aunts_uncles_chart17",
"biological_aunts_uncles_chart18","biological_aunts_uncles_chart19___0",
"biological_aunts_uncles_chart19___1","biological_aunts_uncles_chart20___0",
"biological_aunts_uncles_chart20___1","biological_aunts_uncles_chart21","biological_aunts_uncles_chart22___0","biological_aunts_uncles_chart22___1","biological_aunts_uncles_chart23",
"biological_aunts_uncles_chart24","biological_aunts_uncles_chart25",
"biological_aunts_uncles_chart26","biological_aunts_uncles_chart27___0",
"biological_aunts_uncles_chart27___1","biological_aunts_uncles_chart28___0",
"biological_aunts_uncles_chart28___1","biological_aunts_uncles_chart29",
"biological_aunts_uncles_chart30___0","biological_aunts_uncles_chart30___1",
"biological_aunts_uncles_chart31","biological_aunts_uncles_chart32",
"biological_aunts_uncles_chart33","biological_aunts_uncles_chart34",
"biological_aunts_uncles_chart35___0","biological_aunts_uncles_chart35___1",
"biological_aunts_uncles_chart36___0","biological_aunts_uncles_chart36___1",
"biological_aunts_uncles_chart37","biological_aunts_uncles_chart38___0",
"biological_aunts_uncles_chart38___1","biological_aunts_uncles_chart39",
"biological_aunts_uncles_chart40","biological_aunts_uncles_chart41",
"biological_aunts_uncles_chart42","biological_aunts_uncles_chart43___0",
"biological_aunts_uncles_chart43___1","biological_aunts_uncles_chart44___0",
"biological_aunts_uncles_chart44___1","biological_aunts_uncles_chart45",
"biological_aunts_uncles_chart46___0","biological_aunts_uncles_chart46___1",
"biological_aunts_uncles_chart47","biological_aunts_uncles_chart48",
"biological_aunts_uncles_chart49","biological_aunts_uncles_chart50",
"biological_aunts_uncles_chart51___0","biological_aunts_uncles_chart51___1",
"biological_aunts_uncles_chart52___0","biological_aunts_uncles_chart52___1",
"biological_aunts_uncles_chart53","biological_aunts_uncles_chart54___0",
"biological_aunts_uncles_chart54___1","biological_aunts_uncles_chart55",
"biological_aunts_uncles_chart56","biological_aunts_uncles_chart57",
"biological_aunts_uncles_chart58","biological_aunts_uncles_chart59___0",
"biological_aunts_uncles_chart59___1","biological_aunts_uncles_chart60___0",
"biological_aunts_uncles_chart60___1","biological_aunts_uncles_chart61",
"biological_aunts_uncles_chart62___0","biological_aunts_uncles_chart62___1",
"biological_aunts_uncles_chart63","biological_aunts_uncles_chart64",
"biological_aunts_uncles_chart65","biological_aunts_uncles_chart66",
"biological_aunts_uncles_chart67___0","biological_aunts_uncles_chart67___1",
"biological_aunts_uncles_chart68___0","biological_aunts_uncles_chart68___1",
"biological_aunts_uncles_chart69","biological_aunts_uncles_chart70___0",
"biological_aunts_uncles_chart70___1","biological_aunts_uncles_chart71",
"biological_aunts_uncles_chart72","biological_aunts_uncles_chart73",
"biological_aunts_uncles_chart74","biological_aunts_uncles_chart75___0",
"biological_aunts_uncles_chart75___1","biological_aunts_uncles_chart76___0",
"biological_aunts_uncles_chart76___1","biological_aunts_uncles_chart77",
"biological_aunts_uncles_chart78___0","biological_aunts_uncles_chart78___1",
"biological_aunts_uncles_chart79","biological_aunts_uncles_chart80",
"biological_aunts_uncles_chart81")

PGC_Other_info = c("other_information1___0","other_information1___1","other_information1___2","other_information2","other_information3")
```

```{r List of SGRQ-COPD Questions}
SGRQ_COPD = c("cough_1","cough_2","cough_3","cough_4","cough_5","cough_6","cough_7","cough_8","cough_9","cough_10","shortness_of_breath_2","shortness_of_breath_3","shortness_of_breath_4","shortness_of_breath_5","shortness_of_breath_6","shortness_of_breath_7","shortness_of_breath_8","shortness_of_breath_9","shortness_of_breath_10","shortness_of_breath_11","shortness_of_breath_12","shortness_of_breath_13","shortness_of_breath_14","shortness_of_breath_15",
"shortness_of_breath_16","shortness_of_breath_17","shortness_of_breath_18","shortness_of_breath_19","shortness_of_breath_20","shortness_of_breath_21","shortness_of_breath_22","shortness_of_breath_23","shortness_of_breath_24","shortness_of_breath_25","shortness_of_breath_26",
"shortness_of_breath_27","shortness_of_breath_28","shortness_of_breath_29","shortness_of_breath_30","shortness_of_breath_31","shortness_of_breath_32","shortness_of_breath_33","shortness_of_breath_34","shortness_of_breath_35","shortness_of_breath_36","shortness_of_breath_37",
"shortness_of_breath_38","shortness_of_breath_39","shortness_of_breath_40","shortness_of_breath_41","shortness_of_breath_43","shortness_of_breath_44")
```
```{r List of SGRQ-IPF Items}
SGRQ_IPF = c("cough_11","cough_12","cough_13","cough_14","cough_15","cough_16","shortness_of_breath_47","shortness_of_breath_48","shortness_of_breath_49","shortness_of_breath_50","shortness_of_breath_51","shortness_of_breath_52","shortness_of_breath_53","shortness_of_breath_54","shortness_of_breath_55","shortness_of_breath_56","shortness_of_breath_57","shortness_of_breath_58","shortness_of_breath_59","shortness_of_breath_60","shortness_of_breath_61","shortness_of_breath_62","shortness_of_breath_63","shortness_of_breath_64","shortness_of_breath_65","shortness_of_breath_66","shortness_of_breath_67","shortness_of_breath_68","shortness_of_breath_69","shortness_of_breath_70","shortness_of_breath_71","shortness_of_breath_72","shortness_of_breath_73","shortness_of_breath_74","shortness_of_breath_75")
```


```{r Creates Flags for BubbleStatus in REDCap}
## In REDCap study staff mark complete surveys in the following variable list
REDCap_complete_flags = c("pulmonary_genetics_center_questionnaire_complete","herlihy_questionnaire_complete","ipf_questionnaire_complete","copd_questionnaire_complete")
```

# Loop over all variables in domain
How many participants with modules *MARKED* +missing+?

```{r Creates table of Bubble-Status from REDCap}
REDCap_table_flags = NULL
for (varlist in REDCap_complete_flags){
  REDCap_table_flags[[varlist]]= table(txp[(varlist)])
  print(REDCap_table_flags[varlist])
}
```


```{r}
Herlihy_Completeness_Rheum = NULL
for (varlist in Herlihy_Rheumatology){
  Herlihy_Completeness_Rheum[[varlist]]= table(txp[(varlist)])
  print(Herlihy_Completeness_Rheum[varlist])
  txp$Herli_Rheum= ifelse (is.na(txp[(varlist)]), 1,0)
}
```

Merge in Pulmonary Genetics *ILD* data
```{r}
ALL_Txp = merge(txp, ILD, by= "MRN", all.x = TRUE)
ALL_Txp$PGC_Status = ifelse(is.na(ALL_Txp$PGC_Status.x),
                             ifelse(is.na(ALL_Txp$PGC_Status.y),0,
                                    ALL_Txp$PGC_Status.y),
                             ifelse(ALL_Txp$PGC_Status.x == 0,
                                    ifelse(!is.na(ALL_Txp$PGC_Status.y),
                                           ALL_Txp$PGC_Status.y,ALL_Txp$PGC_Status.x),
                                    ALL_Txp$PGC_Status.x))

ALL_Txp$Herlihy_Status = ifelse(is.na(ALL_Txp$Herlihy_Status.x),
                             ifelse(is.na(ALL_Txp$Herlihy_Status.y),0,
                                    ALL_Txp$Herlihy_Status.y),
                             ifelse(ALL_Txp$Herlihy_Status.x == 0,
                                    ifelse(!is.na(ALL_Txp$Herlihy_Status.y),
                                           ALL_Txp$Herlihy_Status.y,ALL_Txp$Herlihy_Status.x),
                                    ALL_Txp$Herlihy_Status.x))

ALL_Txp$SGRQ_Status = ifelse(is.na(ALL_Txp$SGRQ_Status.x),
                             ifelse(is.na(ALL_Txp$SGRQ_Status.y),0,
                                    ALL_Txp$SGRQ_Status.y),
                             ifelse(ALL_Txp$SGRQ_Status.x == 0,
                                    ifelse(!is.na(ALL_Txp$SGRQ_Status.y),
                                           ALL_Txp$SGRQ_Status.y,ALL_Txp$SGRQ_Status.x),
                                    ALL_Txp$SGRQ_Status.x))
ALL_Txp$AnyMissingSurvey = ifelse((ALL_Txp$SGRQ_Status == 0 | ALL_Txp$Herlihy_Status==0 |ALL_Txp$PGC_Status ==0),
                                  1,0)
KEEP = c("TransplantID","MRN","PGC_Status","Herlihy_Status","SGRQ_Status","PGCS_Status","TransplantStudy","emailAVAIL","email","elig_dx","Deceased","AnyMissingSurvey")
ALL_Txp = ALL_Txp[KEEP]
```
## Shared with ClinGen
```{r}
table(ALL_Txp$TransplantStudy[is.na(ALL_Txp$ClinicalGeneticsStudy)])
```


## MISSING

### How many missing in Transplant DB (n=208)
#### Totally Complete vs missing at least one survey
```{r}
missing_txp_surveys = ifelse(txp$PGC_Status == 0 | txp$Herlihy_Status ==  0 | txp$SGRQ_Status == 0, 1,0)
missing_txp_surveys[is.na(missing_txp_surveys)] = 1
table(missing_txp_surveys)
```



### Of the 124 missing from Transplant REDCap ... how many in ClinGen?  

#### Totally Complete vs missing at least one survey
```{r}
table(ALL_Txp$AnyMissingSurvey)
```

#### Of those 130 missing at least one survey, how many are in ClinGen?

```{r}
table(ALL_Txp$AnyMissingSurvey[ALL_Txp$ClinicalGeneticsStudy])
```
* 40/130 (31%) enrolled in both

### How many TOTALLY complete, how many missing by Survey instrument? 
#### PGC
```{r}
table(ALL_Txp$PGC_Status)
```
#### Herlihy
```{r}
table(ALL_Txp$Herlihy_Status)
```

#### SGRQ
```{r}
table(ALL_Txp$SGRQ_Status)
```
```{r Output Report}
write.csv(ALL_Txp,"/Volumes/redle/Projects/PPMI/Reports/Transplant_SurveyTRACKING.csv")

```


# EXPORT 
```{r}
ALL_Txp$PGC_Status = factor(ALL_Txp$PGC_Status, labels = c("Missing","OK"))
ALL_Txp$SGRQ_Status = factor(ALL_Txp$SGRQ_Status, labels = c("Missing","OK")) 
#ALL_Txp$PGCS_Status = factor(ALL_Txp$PGCS_Status, labels = c("Missing","OK"))
ALL_Txp$Herlihy_Status = factor(ALL_Txp$Herlihy_Status, labels = c("Missing","OK"))
ALL_Txp$emailAVAIL= factor(ALL_Txp$emailAVAIL, labels = c("No","YES"))
ALL_Txp$Deceased[ALL_Txp$Deceased == ""] = 999
ALL_Txp$Deceased = factor(ALL_Txp$Deceased, labels = c("INACTIVE","IE","DECEASED","active"))
ALL_Txp$Herlihy_Status = factor(ALL_Txp$Herlihy_Status, labels = c("Missing","OK"))
ALL_Txp$AnyMissingSurvey = factor(ALL_Txp$AnyMissingSurvey, labels = c("OK","Missing"))
ALL_Txp$elig_dx = factor(ALL_Txp$elig_dx, labels = c("UNKNOWN","IPF","COPD"))
write.csv(ALL_Txp,"/Users/redle/Dropbox (Partners HealthCare)/Channing/PPMI/Data/Survey Audits/MISSING_QC.csv",row.names = FALSE)
```

